XSGRB - The X-shooter GRB afterglow sample

### 2017-01-10 document/XSGRB_sample.tex
Spec plot and intro

Categorized on the basis of their duration and spectral hardness, two main classes of GRBs exist, long and short \citep{Kouveliotou1993}. Now thoroughly established, the connection between long GRBs and supernovae (SNe) \citep{Galama1998, Hjorth2003a, Stanek2003, Woosley2006c} and the association of the location of long GRBs with the most star-forming regions in their host galaxies \citep{Fruchter2006, Svensson2010a}, make a stellar origin a likely explanation for the progenitor system. The seeming metal aversion \citep{Graham2013, Kruhler2015, Perley2016b} in selection of host at low redshift along with theoretical single-progenitor models preferring more pristine starting conditions \citep{Woosley2006d}, paints a picture where the core of a rapidly spinning, massive star undergoes gravitational collapse, although a certain degree of binarity \citep{Fryer2005, Podsiadlowski2010} in the progenitor population is required to explain the host metallicity distribution to super solar values \citep{Niino2011}. The driving engine in short GRBs have been established as the merger of two compact objects \citep{Metzger2010} through the detection of an associated kilonova \citep{Tanvir2013, Berger2013a}.

 see \citet{Levan2016} for recent review.

@@

@@

>>>>

Categorized on the basis of their duration and spectral hardness, two main classes of GRBs exist, long and short \citep{Kouveliotou1993}. Now thoroughly established, the connection between long GRBs and supernovae (SNe) \citep{Galama1998, Hjorth2003a, Stanek2003, Woosley2006c} and the association of the location of long GRBs with the most star-forming regions in their host galaxies \citep{Fruchter2006, Svensson2010a}, make a stellar origin a likely explanation for the progenitor system. The seeming metal aversion \citep{Graham2013, Kruhler2015, Perley2016b} in selection of host at low redshift along with theoretical single-progenitor models preferring more pristine starting conditions \citep{Woosley2006d}, paints a picture where the core of a rapidly spinning, massive star undergoes gravitational collapse, although a certain degree of binarity \citep{Fryer2005, Podsiadlowski2010} in the progenitor population is required to explain the host metallicity distribution to super solar values \citep{Niino2011}, see \citet{Levan2016} for recent review. The driving engine in short GRBs has been established as the merger of two compact objects \citep{Metzger2010} through the detection of an associated kilonova \citep{Tanvir2013a, Berger2013a}. With the advent of the first gravitational wave (GW) detection \cite{Abbott2016a}, the electromagnetic counterpart in the form of a short

GRBs as cosmological probes

Do GRBs trace star formation

Afterglow spectroscopy

Complete samples

Content of paper

@@

\begin{figure*}
	\centerline{\includegraphics[width=0.85\linewidth]{figures/GRB121024A.pdf}}
	\caption{Telluric corrected, normalized spectrum of GRB121024A at $z = 2.300$,
	meant to illustrate the typical data quality. The acquisition magnitude is r =
	20, meaning it is in the brighter end of the sample presented here, but not the
	brightest. The spectrum is rich in absorption, including molecular absorption
	of $H_2$ with the absorption due to \lya is visible at $\sim$ 4000 $\AA$.
	Additionally, three intervening systems are seen in this sightline  This
	spectrum has been analyzed in detail in \citet{Friis2015}. }
	\label{fig:spectrum}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Science data products} \label{products}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this section we describe the data format. Similar to what is done in \citet{Lopez2016}
